% !TEX root = ../../main.tex
~\\[1in] % hack to put space at top.
\textbf{\Huge Acknowledgments}\bigskip

\noindent 

Without the comprehensive support and guidance I have received leading up to and during my tenure at Columbia, this thesis would never have been possible. I have been fortunate to have such an extensive network of people assisting me on my journey, and I offer my most sincere gratitude to all of them. 

I want to especially thank my advisor, John Parsons, for his unwavering support through both my studies and research as a graduate student. While enabling me to pursue my interests, he offered a steady hand to lead me through this challenging endeavor. Through his encouragement, guidance, and insights he has made this work possible, and has set an excellent example as a researcher, and mentor.
I want to extend my thanks to the rest of the Columbia ATLAS group, particularly Gustaaf Brooijmans who freely offered aid and advice. 

Without the endless, selfless help of Kalliopi Iordanidou, from debugging code to navigating bureaucracy to deciphering theory, I can candidly say this work would not have been possible; and so to her I would like to show my deepest appreciation. Despite her many responsibilities, she always found time to offer assistance, share her experiences, and help me keep perspective. I want to express my gratitude to the entire $\ell\nu qq$ team, whose tireless work is the basis of this thesis. I want to thank Ismet Siral for the many fruitful conversations on our tram rides back to Geneva.  

During my first summer of research at Nevis Laboratories, Tim Andeen invested countless hours of support and direction, for which I am sincerely thankful. While completing my service work, the entire ATLAS LAr Operations team was welcoming and patient. I want to thank them for their trust, and for the incredible opportunity to work up-close with the detector and its operation. I express my gratitude to my undergraduate advisor, Matthew Herndon, who helped tremendously in cultivating my interest in particle physics.

I want to thank my friends at Columbia for the many shared experiences, somehow surviving coursework and quals: Felix Clark, Laura Havener, Matt Anthony, Zach Greene. I especially want to thank Russell Smith, who also transplanted to Geneva, for the countless discussions, beers, and slopes. I want to thank my friends in Geneva who made my stay enjoyable: the entire Coulou for adopting me as one of their own, and Martin Adams, Daniel Fazio, Nico Hafner, and Jan Stypka for the many hikes, cheese markets, and adventures. I want to thank my friends from Wisconsin, Stuart Frazier, Chris Pom, Arjun Adusumilli, and Monica Cooley who always reminded me where home truly is, even as we spread out. 

I am deeply grateful for Karoliina Lohiniva: you ground me when I need it the most, and are the most understanding, caring, and thoughtful person I know.  

Finally, I want to express my warmest thanks to my family, in particular my parents, John and Velta, and my sisters, Cheyanne and Kailey. You have inspired me to pursue my dreams, and have afforded me every opportunity to succeed. You have shaped me into the person I am today. 


